---
title: "Citations"
output:
    prettydoc::html_pretty:
      #number_sections: TRUE
      toc: TRUE
      fig_caption: TRUE
      fig_number: TRUE
      toc_depth: 2
      float: TRUE
vignette: >
  %\VignetteIndexEntry{Citations}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include=FALSE}
#library(FungiExpresZ)
```


## List of articles cited FungiExpresZ

## 2021
1. **_Carbon Catabolite Repression in Filamentous Fungi Is Regulated by Phosphorylation of the Transcription Factor CreA._** de Assis LJ, Silva LP, Bayram O, Dowling P, Kniemeyer O, Krüger T, Brakhage AA, Chen Y, Dong L, Tan K, Wong KH, Ries LNA, Goldman GH. 2021. Carbon catabolite repression in filamentous fungi is regulated by phosphorylation of the transcription factor CreA. mBio 12:e03146-20. [Article link](https://doi.org/10.1128/mBio.03146-20.){target="_blank"}

## 2020
1. **_The Aspergillus fumigatus transcription factor RglT is important for gliotoxin biosynthesis and self-protection, and virulence._** Ries LNA, Pardeshi L, Dong Z, Tan K, Steenwyk JL, Colabardini AC, et al. (2020)  PLoS Pathog 16(7): e1008645. [Article link](https://doi.org/10.1371/journal.ppat.1008645){target="_blank"}  

2. **_Genome-wide characterization of AreA function and regulation in Aspergillus nidulans . University of Macau_** Li, A., & Wong, K. (2020). Thesis (Ph.D.). [Link](https://umlibrary.primo.exlibrisgroup.com/permalink/853UOM_INST/1ug6ab4/alma991009890287006306){target="_blank"}


 
## 2019
1. **_Transcriptomic analysis reveals global and temporal transcription changes during Candida glabrata adaptation to an oxidative environment._** P Sethiya, MN Rai, R Rai, C Parsania, K Tan, KH Wong - Fungal Biology, 2019. [Article link](https://www.sciencedirect.com/science/article/pii/S1878614619301795){target="_blank"}
